\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{iccv}
\usepackage{times}
\usepackage[inline]{enumitem}
\usepackage[export]{adjustbox}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}  %
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{calc}
\usepackage{chngcntr}  %
\usepackage{silence}
\WarningFilter{fixltx2e}{fixltx2e is not required}
\usepackage{fixltx2e}
\usepackage{dblfloatfix}  %
\usepackage{framed}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage{pifont}%
\usepackage{placeins}  %
\usepackage{xfrac}  %
\usepackage{subcaption}
\usepackage{makecell}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,fit,backgrounds,calc}
\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref} %
%
\urlstyle{sf}
\usepackage{cleveref} %


\usepackage{multibib}
\newcites{suppl}{Supplemental references}%

\setlength{\tabcolsep}{0.45em}  %

%
\makeatletter
\renewcommand\@makefntext[1]{%
  \noindent\makebox[1em][r]{\@makefnmark}#1}
\makeatother

\input{notations}  %

%
\makeatletter
\renewcommand{\paragraph}{%
  \@startsection{paragraph}{4}%
  %
  {\z@}{0.4em}{-1em}%
  {\normalfont\normalsize\bfseries}%
}

%
\setlist[itemize]{%
labelsep=5pt,%
labelindent=0.4\parindent,%
itemindent=0pt,%
leftmargin=*,%
itemsep=-4pt, 
}

\makeatother

\definecolor{darkgreen}{RGB}{0, 140, 0}
\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
\definecolor{auburn}{rgb}{0.43, 0.21, 0.1}

\newcommand{\rv}[1]{{\color{antiquefuchsia}[\textbf{Rv}:#1]}}
\newcommand{\maxim}[1]{{\color{red}[\textbf{MB}:#1]}}
\newcommand{\matthijs}[1]{{\color{blue}[\textbf{MD}:#1]}}
\newcommand{\av}[1]{{\color{auburn}[\textbf{AV}:#1]}}
\newcommand{\iasonas}[1]{{\color{darkgreen}[\textbf{IK}:#1]}}

%
%
%
%
%
%

\newif\ifarxiv
\global\arxivtrue

\iccvfinalcopy
\ificcvfinal\pagestyle{empty}\fi
%
\def\iccvPaperID{5147}
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\ifarxiv\pagestyle{plain}\fi

%
\title{MultiGrain: a unified image embedding for classes and instances}
\author{\begin{tabular}{ccccc}
  Maxim Berman\thanks{Did this work during an internship at Facebook AI Research.} & Herv\'e J\'egou & Andrea Vedaldi & Iasonas Kokkinos & Matthijs Douze \\
  ESAT--PSI, KU Leuven & \multicolumn{4}{c}{Facebook AI Research} \\
 %
\end{tabular}}

\ificcvfinal
\hypersetup{  %
pdftitle={MultiGrain: a unified image embedding for classes and instances},
pdfsubject={},
pdfauthor={Maxim Berman, Herve Jegou, Andrea Vedaldi, Iasonas Kokkinos, Matthijs Douze} %
pdfkeywords={}
}
\fi

\makeatletter
\let\inserttitle\@title
%
\makeatother

\begin{document}
\maketitle
\begin{abstract}
MultiGrain is a network architecture producing compact vector representations that are suited both for image classification and particular object retrieval. 
It builds on a standard classification trunk.
The top of the network produces an embedding containing coarse and fine-grained information, so that images can be recognized based on the object class, particular object, or if they are distorted copies.
Our joint training is simple: we minimize a  cross-entropy loss for classification and a ranking loss 
that determines if two images are identical up to data augmentation, with no need for additional labels. 
A key component of MultiGrain is a pooling layer that takes advantage of high-resolution images with a network trained at a lower resolution. 

When fed to a linear classifier, the learned embeddings provide state-of-the-art classification accuracy. 
For instance, we obtain 79.4\% top-1 accuracy with a ResNet-50 learned on Imagenet, which is a +1.8\% absolute improvement over the AutoAugment method. 
When compared with the cosine similarity, the same embeddings perform on par with the state-of-the-art for image retrieval at moderate resolutions. 

 %

%
%
%
%
%
%
%
%
\end{abstract}

\input{intro}
\input{related}
\input{archi}
\input{experiments}
\input{conclusions}

\ificcvfinal
\paragraph*{Acknowledgments.} 
We thank Kaiming He for useful feedback and references. 
Maxim Berman is supported by Research Foundation - Flanders (FWO) through project number G0A2716N. PSI--ESAT acknowledges a GPU server donation from FAIR Partnership Program.

\fi
%


{\small\bibliographystyle{ieee}\bibliography{biblio}}

%
%
\input{supplementary}
%
%
\end{document}
