% Template for ICASSP-2018 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\pdfoutput=1
\documentclass{article}
\usepackage{authblk}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{float}
\usepackage[hang,flushmargin]{footmisc}
\usepackage{makecell}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{paralist}
\usepackage{spconf,amsmath,graphicx}
\usepackage{todonotes}
\usepackage{xspace}

\newcommand{\eg}{e.g.,\xspace}
\newcommand{\etc}{etc.\xspace}
\newcommand{\ie}{i.e.,\xspace}

\makeatletter
\renewcommand\AB@affilsepx{, \protect\Affilfont}
\makeatother
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\interfootnotelinepenalty=10000



% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% Title.
% ------
\title{\large \bf Natural TTS Synthesis By Conditioning WaveNet On Mel Spectrogram Predictions}

\renewcommand*{\Authfont}{\itshape}
\author[1]{Jonathan Shen}
\author[1]{Ruoming Pang}
\author[1]{Ron J. Weiss}
\author[1]{Mike Schuster}
\author[1]{Navdeep Jaitly}
\author[2]{Zongheng Yang\thanks{Work done while at Google.}}
\author[1]{Zhifeng Chen}
\author[1]{Yu Zhang}
\author[1]{Yuxuan Wang}
\author[1]{RJ Skerry-Ryan}
\author[1]{Rif A. Saurous}
\author[1]{Yannis Agiomyrgiannakis}
\author[1]{Yonghui Wu}
\affil[1]{Google, Inc.}
\affil[2]{University of California, Berkeley}
\affil[ ]{\texttt{\{jonathanasdf,rpang,yonghui\}@google.com}}
\date{}

\begin{document}
\ninept
%
\maketitle
%

\begin{abstract}
This paper describes Tacotron~2,
a neural network architecture for speech synthesis directly
from text. The system is composed of a recurrent sequence-to-sequence feature
prediction network that maps character embeddings to
mel-scale spectrograms, followed by a modified WaveNet model acting as a vocoder
to synthesize time-domain waveforms from those spectrograms. Our model achieves
a mean opinion score (MOS) of $4.53$ comparable to a MOS of $4.58$ for
professionally recorded speech.
To validate our design choices, we present ablation studies of key components of
our system and evaluate the impact of using mel spectrograms as the conditioning
input to WaveNet instead of linguistic, duration, and $F_0$ features. We further
show that using this compact acoustic intermediate representation allows
for a significant reduction in the size of the WaveNet architecture.
\end{abstract}
%
\begin{keywords}
Tacotron 2, WaveNet, text-to-speech
\end{keywords}
%

%%%%%%%%%%%%%%%%%%%%%
\input{introduction.tex}
%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%
\input{architecture.tex}
%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%
\input{experiments.tex}
%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%
\input{conclusion.tex}
%%%%%%%%%%%%%%%%%%%%%

\section{Acknowledgments}
The authors thank Jan Chorowski, Samy Bengio, A{\"a}ron van den Oord, and the
  WaveNet and Machine Hearing teams for their helpful discussions and advice, as
  well as Heiga Zen and the Google TTS team for their feedback and assistance
  with running evaluations.
  %
  The authors are also grateful to the very thorough reviewers.
% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\bibliographystyle{IEEEbib}
\bibliography{ms}

\end{document}
